```{r, include=F}
library(tidyverse)
library(DBI)
library(RSQLite)

#Load database
wolf_db <- dbConnect(SQLite(), "../wolf.db")

#Load tables
wolf_id <- dbGetQuery(wolf_db, "SELECT * FROM wolf_id;")
harvest <- dbGetQuery(wolf_db, "SELECT * FROM harvest;")
life_history <- dbGetQuery(wolf_db, "SELECT * FROM life_history;")
```

# Data exploration

## Summary statistics

How many wolves in the data set were harvested?

```{r}
harvest %>%
  summarise(total_wolves_harvested = n_distinct(mort_tag))
```
4661 wolves were harvested, according to this database. 

## Data visualization

Here I use ggplot to create reproducible graphs using different elements of the wolf harvest data. 

### How many wolves were harvested each year?

```{r}
harvest %>%
  group_by(harvest_year) %>%
  summarise(animals_harvested = n_distinct(mort_tag)) %>% 
  filter(harvest_year !=2021) %>%
  ggplot(aes(x = factor(harvest_year), 
             y = animals_harvested)) +
  geom_bar(stat = "identity", 
           fill = "gray") + 
  geom_smooth(method = "lm", aes(group = 1), color = "black", se = FALSE) +
  labs(x = "Year", 
       y = "Count") +
  theme_minimal()
```

### How many wolves were harvested by trapping each year?
```{r}
harvest %>%
  filter(mortality_agent == "Trapping", harvest_year != 2021) %>%  
  count(harvest_year, mortality_agent) %>% 
  ggplot(aes(x = factor(harvest_year), 
             y = n, 
             fill = factor(harvest_year))) +  
  geom_bar(stat = "identity", 
           show.legend = F,
           fill = "gray") +
  labs(x = "Year", 
       y = "Count") +
  theme_minimal() 
```

### What were the mortality agents in 2020?

```{r}
harvest %>%
 filter(harvest_year == 2020) %>%  
  count(mortality_agent) %>%  
  ggplot(aes(x = reorder(mortality_agent, n), 
             y = n,
             fill = mortality_agent)) +  
  geom_bar(stat = "identity",
           show.legend = FALSE,
           fill = "gray") +  
  labs(x = "Mortality agent", 
       y = "Count") +
  theme_minimal() 
```



### What methods of harvest were used in 2020?

```{r}
harvest %>%
  filter(harvest_year == 2020) %>%  
  count(Method) %>%  
  ggplot(aes(x = reorder(Method, n), 
             y = n, 
             fill = Method)) +  
  geom_bar(stat = "identity",
           show.legend = F,
           fill = "gray") +  
  labs(x = "Harvest Method", 
       y = "Count") +
  theme_minimal() 
```


### What harvest weapons were used in 2020?

```{r}
harvest %>%
  filter(harvest_year == 2020) %>%  
  count(Weapon) %>%  
  ggplot(aes(x = reorder(Weapon, n), y = n, fill = Weapon)) +  
  geom_bar(stat = "identity",
           show.legend = F,
           fill = "gray") +  
  labs(x = "Weapon", 
       y = "Count") +
  theme_minimal() 
```

